The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-10 ms.tex
Rescaling table entries (a few entries have additional changes...).

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{deluxetable}
% \usepackage{natbib}

@@

\begin{document}
\title{Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
\maketitle

@@

To isolate the physics of interest, our baseline calculations neglect two potentially important effects: heat conduction and radiative cooling.  Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:  
\be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T), \ee
where $\kappa_{\rm
  eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is
the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the
classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in
cgs units).  The flux limitor $\psi = \kappa_{\rm spitz} \nabla
T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free
path for electron coulomb scattering exceeds the
temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the
isothermal sound speed and $\phi \lesssim 1$ is an uncertain
dimensionless constant (we adopt $\phi = 0.1$).  Even a weak magnetic
field that is oriented perpendicular to the flow could suppress the
conductivity by greatly reducing the electron mean free path.  However, for radially-decreasing temperature profiles
of interest, the flow is susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field geometry (\citealt{Parrish&Stone07}).  We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity errors in the key properties of the solutions.

Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}) of the form
\be
\dot{q}_{\rm rad} = -\Lambda(T)n^{2},
\label{eq:qdot_rad}
\ee
where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.  We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low or if the mass return rate $\eta$ is high.  However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that cannot be accounted for by our 1D
time-independent model.  A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).

@@

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ & {comments}\\
\hline
$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
\hline
10$^{6}$ & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
unresolved \\
10$^{6}$ & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ & N & \\
10$^{6}$ & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  N &\\
10$^{7}$ & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
10$^{7}$ & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
10$^{7}$ & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ & N & \\
\hline
10$^{8}$ & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
  -2 }$ & Y  & \\
10$^{8}$ & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
10$^{8}$ & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
  3 }$ & N &  \\
10$^{8}$ & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
10$^{8}$$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
10$^{8}$ & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &Y & TI/convergence \\
%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
%  -3 }$ &  TI/convergence\\
10$^{8}$ & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
10$^{7}$ & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
10$^{7}$ & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
%10^{ -2 }$   & TI/convergence  \\
10$^{7}$ & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
10^{ -2 }$ & Y &TI/convergence \\
10$^{6}$ & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
10^{ 4 }$ & N & \\
10$^{7}$ & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
  3 }$ & N & tried run w rb=100 pc resolved, what would happen if rb=400 pc?\\
10$^{6}$ & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
10$^{7}$ & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
10$^{8}$ & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
10$^{8}$ & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
10$^{8}$ & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
%1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
10$^{8}$ & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
\hline
\label{table:models}  
\end{tabular}
$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in Eddington units, normalized to a stellar mass input parameter $\eta = 0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at stagnation radius.  $^{(e)}$ Is solution thermally unstable?  $\dagger$Calculated including radiative cooling, assuming $\eta = 0.04$.  {\bf BDM: (1) remove comments column, (2) update numbers assuming eta = 0.04, (3) make sure all combinations of vw and mbh are included}
\end{minipage}
\end{table*}

%\begin{table*}
%\centering
%\begin{minipage}{18cm}
%\caption{Comparison of numerical solutions with and without
 % cooling. We have chosen $\eta=0.04$, which one would expect for 
  %the average star formation history for $\Mbh=10^8\Msun$ 
 % (see Figures~\ref{fig:eta} {\bf AG-cite star formation history
  %  figure once it is made.}). Note that we have deliberately chosen a solution
  %near our thermal stability threshold where cooling is beginning
  %to become important.
%}
%\begin{tabular}{lccccccccccccc}
%\hline
%{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma$} & {$r_b$} & {$\eta$} &
%{$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
%\hline
%1 & 300 & 0.8 & 50.0 & 0.04 & $ 3.3 \times 10^{ -4 }$ & 4.6 &  \\
%1 & 300 & 0.8 & 50.0 & 0.04 & $ 9.1 \times 10^{ -4 }$ & 5.6 & \\
%\hline
%\label{table:models}  
%\end{tabular}
%\end{minipage}
%\end{table*}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ in units of the sphere of influence radius $r_{\rm
      soi}$ (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols correspond to different values of $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies ($\Gamma = 0.8$), while
    triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
    analytic prediction from equation (\ref{eq:rs2main}), with solid and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$ and $\{\Gamma=0.1,n=0.5\}$, respectively.  {\bf BDM: is the x axis here $v_{w}$ or $\vw$ !!?  fold $\eta$ into the y axis. }}
\end{figure}

>>>>

\documentclass[usenatbib,fleqn]{mn2e}

\makeatletter
\newlength{\abovecaptionskip}%
\setlength{\abovecaptionskip}{10\p@}
\makeatother
\usepackage{threeparttable}

\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{deluxetable}
% \usepackage{natbib}

@@

\begin{document}
\title{The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
\maketitle

@@

To isolate the physics of interest, our baseline calculations neglect two potentially important effects: heat conduction and radiative cooling.  Electron heat conduction results in an an additional term on the right hand side of the entropy equation of the form:  
\be \dot{q}_{\rm cond} = \nabla\cdot(\kappa \nabla T), \ee
where $\kappa_{\rm
  eff}=\kappa_{\rm spitz}/(1+\psi)$ (\citealt{DaltonBalbus:1993a}) is
the conducitivity and $\kappa_{\rm spitz} = \kappa_0 T^{5/2}$ is the
classical \citet{Spitzer62} value ($\kappa_0\simeq 2\times 10^{-6}$ in
cgs units).  The flux limitor $\psi = \kappa_{\rm spitz} \nabla
T/(5\phi \rho c_s^3)$ saturates the conductive flux if the mean free
path for electron coulomb scattering exceeds the
temperature length scale, where $c_s \equiv (kT/\mu m_p)^{1/2}$ is the
isothermal sound speed and $\phi \lesssim 1$ is an uncertain
dimensionless constant (we adopt $\phi = 0.1$).  Even a weak magnetic
field that is oriented perpendicular to the flow could suppress the
conductivity by greatly reducing the electron mean free path.  However, for radially-decreasing temperature profiles
of interest, the flow is susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field geometry (\citealt{Parrish&Stone07}).  We show later in $\S\ref{sec:conductivity}$ that neglecting conductivity results in at most only order-unity corrections to the key properties of solutions calculated assuming its presence.

Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}) of the form
\be
\dot{q}_{\rm rad} = -\Lambda(T)n^{2},
\label{eq:qdot_rad}
\ee
where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.  We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.  However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instability (e.g.~\citealt{McCourt+12}) that our 1D
time-independent model cannot account for anyways.  A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).

@@

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ \\
\hline
$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
\hline
$    10^{ 6 }$ & 300 & 0.8 & $>$ & $ 1.3 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ & No \\
$    10^{ 6 }$ & 600 & 0.8 & $>$ & $ 2.2 \times 10^{ -6 }$ & $ 8. 10^{ 3 }$ & No \\
$    10^{ 6 }$ & 1200 & 0.8 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -4 }$ & 6.5 & No \\
$    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.8 & $>$ & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & 1.4 & Yes \\
$    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 & No \\
$    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & 4.7 & Yes \\
$    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & 1.2 & Yes \\
$    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ & 4.6 & Yes\\
$10^{8}\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & Yes & \\
$    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ & 0.43 & Yes \\
$    10^{ 6 }$ & 1200 & 0.1 & $>$ & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.1 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & 4.6 & Yes \\
\hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  $^{(e)}$ Is solution thermally unstable?
$\dagger$Calculated including radiative cooling, assuming $\eta =
0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
  are included. AG: Realized that the solution I ran earlier, with
  cooling was actually a solution that would be thermally unstable
  according to our thermal instability. I am worried that this
  solution may not be representative due to the small break radius.}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

\end{table*}

% \begin{table*}
% \centering
% \begin{minipage}{18cm}
% \caption{Summary of Numerical Solutions}
% \begin{tabular}{lccccccccccccc}
% \hline
% {$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
% {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ & {comments}\\
% \hline
% $(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
% \hline
% 10$^{6}$ & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
% unresolved \\
% 10$^{6}$ & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
% 10^{ 2 }$ & N & \\
% 10$^{6}$ & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
% 10^{ 4 }$ &  N &\\
% 10$^{7}$ & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
% 10$^{7}$ & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
% 10$^{7}$ & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
% 10^{ 3 }$ & N & \\
% \hline
% 10$^{8}$ & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
%   -2 }$ & Y  & \\
% 10$^{8}$ & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
% 10$^{8}$ & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
%   3 }$ & N &  \\
% 10$^{8}$ & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
% 10$^{8}$$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
% 10$^{8}$ & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
%   -2 }$ &Y & TI/convergence \\
% %1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
% %  -3 }$ &  TI/convergence\\
% 10$^{8}$ & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
% 10$^{7}$ & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
% 10$^{7}$ & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
% %0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
% %10^{ -2 }$   & TI/convergence  \\
% 10$^{7}$ & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
% 10^{ -2 }$ & Y &TI/convergence \\
% 10$^{6}$ & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
% 10^{ 4 }$ & N & \\
% 10$^{7}$ & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
%   3 }$ & N & tried run w rb=100 pc resolved, what would happen if rb=400 pc?\\
% 10$^{6}$ & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
% 10$^{7}$ & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
% 10$^{8}$ & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
% 10$^{8}$ & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
% 10$^{8}$ & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
% %1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
% 10$^{8}$ & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
% \hline
% \label{table:models}  
% \end{tabular}
% $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in Eddington units, normalized to a stellar mass input parameter $\eta = 0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at stagnation radius.  $^{(e)}$ Is solution thermally unstable?  $\dagger$Calculated including radiative cooling, assuming $\eta = 0.04$.  {\bf BDM: (1) remove comments column, (2) update numbers assuming eta = 0.04, (3) make sure all combinations of vw and mbh are included}
% \end{minipage}
% \end{table*}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ in units of the sphere of influence radius $r_{\rm
      soi}$ (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols correspond to different values of $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies ($\Gamma = 0.8$), while
    triangles correspond to cores ($\Gamma = 0.1$). The black curves correspond to the
    analytic prediction from equation (\ref{eq:rs2main}), with solid
    and dashed curves calculated for parameters $\{\Gamma=0.8, n=1\}$
    and $\{\Gamma=0.1,n=0.5\}$, respectively.  {\bf BDM: is the x axis
      here $v_{w}$ or $\vw$ !!?  fold $\eta$ into the y axis. AG: The
      axis here is $v_{w}$--it does not include the contribution from
      sigma. Should it be changed}}
\end{figure}
